Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-11 manuscripts/paper-1/main.tex
Better table, some modifications

    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified, listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Table~\ref{tab:Table2})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 24\% of the quality issues of the digital twin were related to the correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
    and finally, 28\% were related to evolvability.

@@

    ~\label{tab:Table2}
    ~\caption{Findings from each Artifact}
    \begin{tabular}{lrr}
        \toprule
        \textbf{Artifact Tree}\\
        \midrule
        \DTsetlength{0.2em}{0.5em}{0.5em}{0.4pt}{1pt}
        \begin{minipage}{5cm}\dirtree{%

@@

        .2 Requirement Specification.

@@

@@

        \end{minipage}

@@

@@

@@

@@

@@

>>>>

    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified, listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Table~\ref{tab:Table2})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 24\% of the quality issues of the digital twin were related to correctness, 35\%  were related to completeness, 8\%  were related to fidelity, 5\%  were related to efficiency,
    and finally, 28\% were related to evolvability.

    \subsection{Example Findings}

    To Three examples illustrate the potential 
    12 - Conceptual Model
    17 - Simulation Model
    20 - Simulation Model
    First: the discrete event simulation model originally enforced a strictly sequential execution of operations.
    However, the human and the cobot can work in parallel, and therefore execute operations also in parallel.
    This issue has been solved already in a later version of the discrete event simulation model.

    F12 - **Even though the durations of the macro-operations were well-known and studied throughly before, the durations of the micro-operations were estimated based on a simple calculation scheme. **Completeness, Correctness.****

    This issue is related to the correctness and completeness of the operational conceptual model. While the durations of the macro-operations are well-known and derived from a previous study, the durations of the micro-operations are estimated based on a simple calculation scheme. This introduces a risk of inaccuracy and incompleteness in the model, which could affect the overall performance of the digital twin. Validating the durations of the micro-operations is necessary to ensure the correctness and completeness of the model, but this validation might not be feasible until the entire
    FELICE system is operational and proper data can be collected. Therefore, this issue should be addressed in the future to ensure the accuracy of the digital twin.

    **F17 - The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.
    **Correctness, Completeness****

    Second: The original discrete event simulation model originally enforced a fixed number of operations per workstation.
    This might be okay for now, but what if the workstations and the workflows change in the future?
    In such cases, adapting the discrete event simulation model might take a substantial some effort.

    **This finding relates to the completeness and fidelity aspects of the DES module. The durations of micro-operations as well as the loading 
    and unloading operations of the cobot are important factors that affect the accuracy of the simulation. The fact that these values are based 
    on assumptions rather than actual measurements means that there is a risk of inaccuracy in the simulation results. In terms of completeness, 
    the module is not able to provide a fully accurate simulation because it is based on assumptions that have not been validated. 
    In terms of fidelity, the module may not accurately reflect the behavior of the real system due to the potential inaccuracy of these assumptions.
    However, it should be noted that this issue is due to limitations in the data collection process rather than any shortcomings in the design of the DES module itself.**

    F20 - **Number of micro-operations were hardcoded, consequently, the DES module must be reprogrammed everytime, when a new micro-operation is needed.** 
    **Evolvability**

    **Based on the given finding, the issue with the process logic section is related to its maintainability and adaptability. 
    The DES module has a hardcoded number of micro-operations that can be performed at a single workstation, which means that the module must be reprogrammed every time 
    a different number of micro-operations is required. This issue could impact the maintainability and adaptability of the DES module. It is suggested that the number of 
    micro-operations per workstation can be configured instead to address this issue. However, it is also mentioned that the current number of micro- 
    and macro-operations allows the generation of 272 workflows, which provides a solid base for look-ahead and optimization purposes and what-if analysis to be executed by a human end-user.**

    Third: The different workflow variants, that can be executed on the assembly line, are managed entirely manually.
    However, the workflow variants mostly differ in the assignment of operations to human and cobot.
    Therefore, one can imagine a technique to generate workflow variants automatically, which would greatly improve evolvability.

@@

    \label{tab:Table2}
    \caption{adfasdfadf}
    \scalebox{0.8}{
        \begin{tabular}{llllll}
            \multicolumn{1}{c} {Findings} & \multicolumn{1}{c} {\textbf{\textit{Correctness}}} & \multicolumn{1}{c}{\textbf{\textit{Completeness}}} 
            & \multicolumn{1}{c}{\textbf{\textit{Fidelity}}} & \multicolumn{1}{c}{\textbf{\textit{Efficiency}}} & \multicolumn{1}{c}{\textbf{\textit{Evolvability}}} \\
            \begin{minipage}{4cm}\dirtree{%

@@

                .2 Requirement Spec.

@@

            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
            }\end{minipage}
            &
            \DTsetlength{0pt}{0pt}{0pt}{0pt}{0pt}
            \begin{minipage}{2cm}\dirtree{%
                .1 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .2 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
                .3 ~~~~~x.
            }\end{minipage}

@@

@@

        \textbf{Process Videos}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\

@@

        \textbf{Scope Definition}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\

@@

        \textbf{Requirement Specification}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\

@@

        \textbf{Conceptual Model}&~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\

@@

        \textbf{Simulation Model} &~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ & ~~~~~~~~~~~~~~~~~~~ \\
